---
title: "Practical Machine Learning Project"
author: "Guoliang Ding"
date: "September 27, 2015"
output: html_document
---

# Introduction

Using devices such as Jawbone Up, Nike FuelBand, and Fitbit it is now possible to collect a large amount of data about personal activity relatively inexpensively. These type of devices are part of the quantified self movement - a group of enthusiasts who take measurements about themselves regularly to improve their health, to find patterns in their behavior, or because they are tech geeks. One thing that people regularly do is quantify how much of a particular activity they do, but they rarely quantify how well they do it.

In this project, we will use data from accelerometers on the belt, forearm, arm, and dumbell of 6 participants to predict the manner in which they did the exercise.

# Data Processing
## Read Data
The data has been pre-downloaded and stored in the working directory
```{r results='hide', message=FALSE, warning=FALSE}
library(caret)
library(randomForest)
library(dplyr)
library(rattle)
```

```{r}
setwd("C:/Users/kilading/Documents/RLearning/Machine")
train <- read.csv(file = "pml-training.csv", na.strings = c("NA", "", "#DIV/0!"))
test <- read.csv(file = "pml-testing.csv", na.strings = c("NA", "", "#DIV/0!"))
```
## Clean Data
### Remove NA values
```{r}
trainRemoveNA <- select(train, which(colSums(is.na(train)) == 0))
testRemoveNA <- select(test, which(colSums(is.na(test)) == 0))
```
### Remove Useless Column
```{r}
trainClean <- select(trainRemoveNA, -c(1, 3, 4, 5, 6, 7))
testClean <- select(testRemoveNA, -c(1, 3, 4, 5, 6, 7))
dim(trainClean)
dim(testClean)
```
## Slice the data
The trainClean data is split into a training data set (70%) and a validation data set (30%)
```{r}
set.seed(100)
inTrain <- createDataPartition(trainClean$classe, p=0.70, list=F)
trainData <- trainClean[inTrain, ]
testData <- trainClean[-inTrain, ]
```
# Modeling
## Build the model with Random Forest
```{r}
controlRf <- trainControl(method="cv", 4)
model <- train(classe ~ ., data=trainData, method="rf", trControl=controlRf, ntree=250)
model
```
## Test on cross validation data set
```{r}
predict <- predict(model, testData)
confusionMatrix(testData$classe, predict)
```
# Predicting
```{r}
result <- predict(model, testClean[, -length(names(testClean))])
result
```